---
title: "R Notebook G 447614 BAM Thesis - Correlations with significance level"
author: "447614"
output: html_notebook
---
20-07-2022

#-------------------------------------------------------------------------------
# Packages
#-------------------------------------------------------------------------------
```{r}
library("tidymodels")
library("readr")
library("stargazer")
library("dplyr")
library("DescTools")
library("glmnet")
library("leaps")
library("xgboost")
library("themis")
library("knitr")
library("ranger")
library("doParallel")
library("vip")
library("ggridges")
library("skimr")
library("forcats")
library("corrplot")
library("readr")
library("neuralnet")
library('fastDummies')
library('xtable')
```

#-------------------------------------------------------------------------------
# Data
#-------------------------------------------------------------------------------
Loading the data:
```{r}
tt_sub_final_w_n <- readRDS(file = "tt_sub_final_w_n.rds")
head(tt_sub_final_w_n)
```

Checking the descriptive statistics:
```{r}
stargazer(tt_sub_final_w_n, type="text", median = TRUE)
```

Including the dummies:
```{r}
tt_sub_final_w_n_dummies <- dummy_cols(tt_sub_final_w_n, select_columns= 'Sector', remove_first_dummy = FALSE)
tt_sub_final_w_n_dummies <- dummy_cols(tt_sub_final_w_n_dummies, select_columns= 'Country', remove_first_dummy = FALSE)
```

#-------------------------------------------------------------------------------
# Significance ESG score & features
#-------------------------------------------------------------------------------

*Receivables turnover ratio*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Receivables turnover ratio`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Receivables turnover ratio`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Working capital turnover ratio*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Working capital turnover ratio`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Working capital turnover ratio`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Total asset turnover ratio*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Total asset turnover ratio`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Total asset turnover ratio`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Gross profit margin*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Gross profit margin`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Gross profit margin`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Net profit margin*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Net profit margin`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Net profit margin`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Current ratio*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Current ratio`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Current ratio`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Debt-to-assets ratio*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Debt-to-assets ratio`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Debt-to-assets ratio`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Debt-to-EBITDA ratio*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Debt-to-EBITDA ratio`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Debt-to-EBITDA ratio`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Interest coverage ratio*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Interest coverage ratio`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Interest coverage ratio`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Price-to-earnings ratio*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Price-to-earnings ratio`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Price-to-earnings ratio`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Earnings per share*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Earnings per share`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Earnings per share`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Dividend yield*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Dividend yield`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Dividend yield`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Market capitalisation*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Market capitalisation`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Market capitalisation`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Number of employees*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Number of employees`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Number of employees`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Total assets*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Total assets`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Total assets`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Stock volatility*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Stock volatility`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Stock volatility`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*ESG data availability low*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`ESG data availability low`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`ESG data availability low`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*ESG data availability middle*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`ESG data availability middle`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`ESG data availability middle`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*ESG data availability high*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`ESG data availability high`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`ESG data availability high`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

#-------------------------------------------------------------------------------

*Sector_Aerospace_and_Defense*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Aerospace_and_Defense`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Aerospace_and_Defense`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Automobiles_and_Parts*  
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Automobiles_and_Parts`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Automobiles_and_Parts`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Beverages*  
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Beverages`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Beverages`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Chemicals*   
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Chemicals`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Chemicals`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Construction_and_Materials*  
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Construction_and_Materials`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Construction_and_Materials`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Consumer_Services*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Consumer_Services`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Consumer_Services`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Electricity* 
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Electricity`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Electricity`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Electronic_and_Electrical_Equipment* 
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Electronic_and_Electrical_Equipment`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Electronic_and_Electrical_Equipment`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Food_Producers*     
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Food_Producers`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Food_Producers`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Gas_Water_and_Multi_utilities* 
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Gas_Water_and_Multi_utilities`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Gas_Water_and_Multi_utilities`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_General_Industrials*     
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_General_Industrials`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_General_Industrials`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Health_Care_Providers*    
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Health_Care_Providers`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Health_Care_Providers`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Household_Goods_and_Home_Construction* 
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Household_Goods_and_Home_Construction`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Household_Goods_and_Home_Construction`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Industrial_Engineering*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Engineering`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Engineering`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Industrial_Materials* 
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Materials`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Materials`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Industrial_Metals_and_Mining*  
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Metals_and_Mining`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Metals_and_Mining`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Industrial_Support_Services*    
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Support_Services`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Support_Services`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Industrial_Transportation*   
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Transportation`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Industrial_Transportation`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Leisure_Goods*    
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Leisure_Goods`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Leisure_Goods`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Media*              
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Media`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Media`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Medical_Equipment_and_Services*  
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Medical_Equipment_and_Services`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Medical_Equipment_and_Services`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Oil_Gas_and_Coal*    
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Oil_Gas_and_Coal`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Oil_Gas_and_Coal`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Other*                              
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Other`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Other`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Personal_Care_Drug_and_Grocery_Stores*
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Personal_Care_Drug_and_Grocery_Stores`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Personal_Care_Drug_and_Grocery_Stores`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Personal_Goods*     
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Personal_Goods`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Personal_Goods`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Pharmaceuticals_and_Biotechnology*   
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Pharmaceuticals_and_Biotechnology`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Pharmaceuticals_and_Biotechnology`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Retailers*         
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Retailers`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Retailers`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Software_and_Computer_Services*     
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Software_and_Computer_Services`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Software_and_Computer_Services`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Technology_Hardware_and_Equipment*   
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Technology_Hardware_and_Equipment`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Technology_Hardware_and_Equipment`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Telecommunications_Equipment*       
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Telecommunications_Equipment`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Telecommunications_Equipment`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Telecommunications_Service_Providers*  
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Telecommunications_Service_Providers`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Telecommunications_Service_Providers`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Sector_Travel_and_Leisure*  
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Travel_and_Leisure`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Sector_Travel_and_Leisure`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_AT*                   
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_AT`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_AT`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_BE*         
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_BE`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_BE`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_CH*                     
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_CH`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_CH`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_DE*          
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_DE`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_DE`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_DK*            
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_DK`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_DK`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_ES*             
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_ES`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_ES`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_FI*                   
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_FI`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_FI`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_FR*       
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_FR`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_FR`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_GB*            
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_GB`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_GB`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_IT*       
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_IT`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_IT`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_NL*            
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_NL`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_NL`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_NO*       
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_NO`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_NO`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_Other*    
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_Other`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_Other`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_SE*              
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_SE`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_SE`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*Country_US* 
```{r}
round(cor(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_US`),3)
res <- cor.test(tt_sub_final_w_n_dummies$`ESG score`, tt_sub_final_w_n_dummies$`Country_US`, 
                    method = "pearson")

res
print("The p-values is:")
res$p.value
ifelse(res$p.value<0.001,"3-stars",ifelse(res$p.value<0.01,"2-stars", ifelse(res$p.value<0.05,"1-star",NA)))
```

*End*




