---
title: "R Notebook A 447614 BAM Thesis - Data cleaning"
author: "447614"
output: html_notebook
---
04-07-2022

#-------------------------------------------------------------------------------
#Packages
#-------------------------------------------------------------------------------
Loading the packages:
```{r}
library("tidymodels")
library("readr")
library("stargazer")
library("dplyr")
library("DescTools")
library("glmnet")
library("leaps")
library("xgboost")
library("themis")
library("knitr")
library("ranger")
library("doParallel")
library("vip")
library("ggridges")
library("skimr")
library("forcats")
library("corrplot")
library("readr")
library("neuralnet")
library('fastDummies')
library('xtable')
```

#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------
*Train test data set*
#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------

#-------------------------------------------------------------------------------
#Data
#-------------------------------------------------------------------------------
Loading the data:
```{r}
tt <- read.csv("Train_test_data_set_FINAL.csv", sep = ";")
head(tt)
```

```{r}
glimpse(tt)
```

#-------------------------------------------------------------------------------
#Creating the ESG quartile variable
#-------------------------------------------------------------------------------
```{r}
tt$ESG_quartile <- NA

tt$ESG_quartile <- ifelse(
  tt$ESG_score_2020 <= 25, 1, 
  ifelse(
    (tt$ESG_score_2020 > 25) & (tt$ESG_score_2020 <= 50), 2, 
    ifelse(
      (tt$ESG_score_2020 > 50) & (tt$ESG_score_2020 <= 75),
      3,
      ifelse(
        (tt$ESG_score_2020 > 75) & (tt$ESG_score_2020 <= 100),
        4, NA))))
```


#-------------------------------------------------------------------------------
#Variables overview
#-------------------------------------------------------------------------------

*Dependent variable:* 
ESG_score_2020
decile_multiclass
ESG_quartile

*Independent variables:*

*Activity:*
receivables_turnover
working_capital_turnover
total_asset_turnover

*Profitability:*
gross_profit_margin
net_profit_margin

*Liquidity:*
current_ratio

*Solvency:*
debt_to_assets
debt_to_ebitda
interest_coverage

*Valuation:*
price_to_earnings
eps
dividend_yield

*Size measures:*
market_cap
n_employees
total_assets

*Stock characteristics*
icb_sector_name
country
stock_volatility_2020

*ESG data availability*
esg_data_availability

19 predictors, 3 dependent variables, total = 22

#-------------------------------------------------------------------------------
#Summary statistics
#-------------------------------------------------------------------------------
```{r}
skim(tt) %>% knit_print()
```
There are no missing values.

#-------------------------------------------------------------------------------
#Sub selection including only relevant features and dependent variables
#-------------------------------------------------------------------------------
```{r}
subset_tt <- c("ISIN", "ESG_score_2020", "decile_multiclass", "ESG_quartile","receivables_turnover", 
               "working_capital_turnover", "total_asset_turnover",
               "gross_profit_margin", "net_profit_margin", 
               "current_ratio", "debt_to_assets", 
               "debt_to_ebitda", "interest_coverage",
               "price_to_earnings", "eps", "dividend_yield",
               "market_cap", "n_employees", "total_assets",
               "icb_sector_name", 
               "country", "stock_volatility_2020",
               "esg_data_availability"
               )
tt_sub_final <- tt[subset_tt]
```

#-------------------------------------------------------------------------------
#Correlation matrix & multicollinearity:
#-------------------------------------------------------------------------------
Creating a correlation matrix:
```{r}
tt_sub_final %>% select_if(is.numeric) %>% 
  cor() %>% corrplot()
```
Very high correlations are absent.

#-------------------------------------------------------------------------------
#Checking the frequencies of categorical variables and solving problems
#-------------------------------------------------------------------------------
Too small frequencies result in overfitting.

Checking for the variables:
*country*
*icb_sector_name*

Length = 2,263 stocks
1% is considered as the minimum acceptable frequency which is approximately 23.

*country*
For this feature, the frequencies are for some values problematic as it is sometimes less than 23, resulting in a frequency of less than 1%.
```{r}
table(tt_sub_final$country) 
table(tt_sub_final$country) / length(tt_sub_final$country)
```

Rule: <1% -> regroup to "Other"
BM
CZ
GI
GR
HU
IE
IM
JE
LU
MT
PL
PT

Regrouping the values with a frequency of <1% to the category other:
```{r}
tt_sub_final$country <- recode(tt_sub_final$country, 
       BM = "Other", 
       CZ = "Other", 
       GI = "Other", 
       GR = "Other", 
       HU = "Other", 
       IE = "Other", 
       IM = "Other", 
       JE = "Other",
       MT = "Other",
       PL = "Other",
       PT = "Other",
       LU = "Other")
```

Checking whether it works:
```{r}
table(tt_sub_final$country) 
table(tt_sub_final$country) / length(tt_sub_final$country)
```
It worked.

*icb_sector_name*
For this feature, the frequencies are for some values problematic as it is sometimes less than 23, resulting in a frequency of less than 1%.

Removing the spaces, - , and commas.
```{r}
tt_sub_final$icb_sector_name <- gsub(" ", "_", tt_sub_final$icb_sector_name)
tt_sub_final$icb_sector_name <- gsub("-", "_", tt_sub_final$icb_sector_name)
tt_sub_final$icb_sector_name <- gsub(",", "", tt_sub_final$icb_sector_name)
```

Showing the frequencies:
```{r}
table(tt_sub_final$icb_sector_name)
```

Rule: <1% (23) -> regroup to other:
Investment_Banking_and_Brokerage_Services
Non_life_Insurance
Open_End_and_Miscellaneous_Investment_Vehicles
Precious_Metals_and_Mining
Real_Estate_Investment_Trusts
Tobacco
Waste_and_Disposal_Services
Alternative_Energy
Finance_and_Credit_Services
Real_Estate_Investment_and_Services

Regrouping the values with a frequency of <1% to the category other:
```{r}
tt_sub_final$icb_sector_name <- recode(tt_sub_final$icb_sector_name,
       Investment_Banking_and_Brokerage_Services = "Other",
       Non_life_Insurance = "Other",
       Open_End_and_Miscellaneous_Investment_Vehicles = "Other",
       Precious_Metals_and_Mining = "Other",
       Real_Estate_Investment_Trusts = "Other",
       Tobacco = "Other",
       Waste_and_Disposal_Services = "Other",
       Alternative_Energy = "Other",
       Finance_and_Credit_Services = "Other",
       Real_Estate_Investment_and_Services = "Other")
```


Checking whether it worked:
```{r}
table(tt_sub_final$icb_sector_name)
```
It worked.

#-------------------------------------------------------------------------------
#Adjustments for percentages
#-------------------------------------------------------------------------------
Descriptive statistics before the adjustments:
```{r}
stargazer(tt_sub_final, type="text")
```

Gross profit margin, net profit margin, debt to assets, and dividend yield are in percentage points. The following adjustments result in a percentage:
```{r}
tt_sub_final$gross_profit_margin <- tt_sub_final$gross_profit_margin / 100
tt_sub_final$net_profit_margin <- tt_sub_final$net_profit_margin / 100
tt_sub_final$debt_to_assets <- tt_sub_final$debt_to_assets / 100
tt_sub_final$dividend_yield <- tt_sub_final$dividend_yield / 100
```

```{r}
stargazer(tt_sub_final, type="text", median = TRUE)
```

#-------------------------------------------------------------------------------
#Checking for skewness, winsorizing, and log transformation through histograms
#-------------------------------------------------------------------------------
Constructing a histogram for each variable:
```{r}
#ESG_score_2020
tt_sub_final %>% ggplot(aes(x = ESG_score_2020)) + geom_histogram()
#decile_multiclass
tt_sub_final %>% ggplot(aes(x = decile_multiclass)) + geom_histogram()
#ESG_quartile
tt_sub_final %>% ggplot(aes(x = ESG_quartile)) + geom_histogram()
#receivables_turnover                                      
tt_sub_final %>% ggplot(aes(x = receivables_turnover)) + geom_histogram()
#working_capital_turnover                                 
tt_sub_final %>% ggplot(aes(x = working_capital_turnover)) + geom_histogram()
#total_asset_turnover
tt_sub_final %>% ggplot(aes(x = total_asset_turnover)) + geom_histogram()
#gross_profit_margin                                        
tt_sub_final %>% ggplot(aes(x = gross_profit_margin)) + geom_histogram()
#net_profit_margin                                          
tt_sub_final %>% ggplot(aes(x = net_profit_margin)) + geom_histogram()
#current_ratio                                             
tt_sub_final %>% ggplot(aes(x = current_ratio)) + geom_histogram()
#debt_to_assets                                           
tt_sub_final %>% ggplot(aes(x = debt_to_assets)) + geom_histogram()
#debt_to_ebitda                                             
tt_sub_final %>% ggplot(aes(x = debt_to_ebitda)) + geom_histogram()
#interest_coverage
tt_sub_final %>% ggplot(aes(x = interest_coverage)) + geom_histogram()
#price_to_earnings                                           
tt_sub_final %>% ggplot(aes(x = price_to_earnings)) + geom_histogram()
#eps                                                          
tt_sub_final %>% ggplot(aes(x = eps)) + geom_histogram()
#dividend_yield                                               
tt_sub_final %>% ggplot(aes(x = dividend_yield)) + geom_histogram()
#market_cap                                                   
tt_sub_final %>% ggplot(aes(x = market_cap)) + geom_histogram()
#n_employees                                                  
tt_sub_final %>% ggplot(aes(x = n_employees)) + geom_histogram()
#total_assets                                               
tt_sub_final %>% ggplot(aes(x = total_assets)) + geom_histogram()
#stock_volatility_2020                                        
tt_sub_final %>% ggplot(aes(x = stock_volatility_2020)) + geom_histogram()
#esg_data_availability                                        
tt_sub_final %>% ggplot(aes(x = esg_data_availability)) + geom_histogram()
```
*1* ESG_score_2020:                 Winsorize: NO      Log Transform: NO
*2* decile_multiclass:              Winsorize: NO      Log Transform: NO
*3* ESG_quartile:                   Winsorize: NO      Log Transform: NO
*4* receivables_turnover:           Winsorize: YES     Log Transform: NO (RATIO)
*5* working_capital_turnover:       Winsorize: YES     Log Transform: NO (RATIO)
*6* total_asset_turnover:           Winsorize: YES     Log Transform: NO (RATIO)
*7* gross_profit_margin:            Winsorize: YES     Log Transform: NO (RATIO)        
*8* net_profit_margin:              Winsorize: YES     Log Transform: NO (RATIO) 
*9* current_ratio:                  Winsorize: YES     Log Transform: NO (RATIO)
*10* debt_to_assets:                Winsorize: YES     Log Transform: NO (RATIO)
*11* debt_to_ebitda:                Winsorize: YES     Log Transform: NO (RATIO) 
*12* interest_coverage:             Winsorize: YES     Log Transform: NO (RATIO)
*13* price_to_earnings:             Winsorize: YES     Log Transform: NO (RATIO)
*14* eps:                           Winsorize: YES     Log Transform: NO (RATIO)
*15* dividend_yield:                Winsorize: YES     Log Transform: NO (RATIO)
*16* market_cap:                    Winsorize: YES     Log Transform: YES
*17* n_employees:                   Winsorize: YES     Log Transform: YES
*18* total_assets:                  Winsorize: YES     Log Transform: YES
*19* stock_volatility_2020:         Winsorize: YES     Log Transform: YES
*20* esg_data_availability:         Convert to dummies 
*21* icb_sector_name                Use as dummies (step_dummy)
*22* country                        Use as dummies (step_dummy)

#-------------------------------------------------------------------------------
#Converting ESG data availability to dummies
#-------------------------------------------------------------------------------
Creating dummies (always skip one dummy unless it involves a decision tree).
0 only has a frequency of 2 -> regroup to low(0 and 0.76) middle(0.95) and high (1).
```{r}
tt_sub_final$esg_data_availability_low <- ifelse(
  (round(tt_sub_final$esg_data_availability,2) == 0.76) | 
    (tt_sub_final$esg_data_availability == 0.0000000), 1, 0)
tt_sub_final$esg_data_availability_middle <- ifelse(
  round(tt_sub_final$esg_data_availability,2) == 0.95, 1, 0)
tt_sub_final$esg_data_availability_high <- ifelse(
  tt_sub_final$esg_data_availability == 1.0000000, 1, 0)
```

Checking their frequencies:
```{r}
table(tt_sub_final$esg_data_availability_low)
table(tt_sub_final$esg_data_availability_middle)
table(tt_sub_final$esg_data_availability_high)
```
Correct, it works and the sum of 1 is 2,263.

#-------------------------------------------------------------------------------
#Conclusion for variable transformation
#-------------------------------------------------------------------------------

*Log transform:* -> in recipe
market_cap 
n_employees
total_assets
stock_volatility_2020

*Winsorize:*
ALL numeric except dependent variable ESG, ESG decile (decile_multiclass), 
and ESG quartile

*Step_dummy:* -> in recipe
icb_sector_name
country

*Normalize* -> in recipe
All, except dependent variable ESG

#-------------------------------------------------------------------------------
#Winsorizing
#-------------------------------------------------------------------------------
Cannot be done in recipe and want winsorized descriptive statistics.

*The following variables:*
*w4* receivables_turnover       1%
*w5* working_capital_turnover   1%
*w6* total_asset_turnover       1%
*w7* gross_profit_margin        1%
*w8* net_profit_margin          2.5%
*w9* current_ratio              1%
*w10* debt_to_assets            1%
*w11* debt_to_ebitda            1%  
*w12* interest_coverage         2.5%
*w13* price_to_earnings         2.5%
*w14* eps                       2.5%
*w15* dividend_yield            1%
*w16* market_cap                1%
*w17* n_employees               1%
*w18* total_assets              2.5%
*w19* stock_volatility_2020     1%

Creating a new dataframe (unwinsorized is stored in the previous one):
```{r}
tt_sub_final_w <- tt_sub_final
```

*w4* receivables_turnover
```{r}
tt_sub_final_w$receivables_turnover <- 
  Winsorize(tt_sub_final_w$receivables_turnover, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$receivables_turnover)
hist(tt_sub_final_w$receivables_turnover)
```

*w5* working_capital_turnover 
```{r}
tt_sub_final_w$working_capital_turnover <- 
  Winsorize(tt_sub_final_w$working_capital_turnover, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$working_capital_turnover)
hist(tt_sub_final_w$working_capital_turnover)
```

*w6* total_asset_turnover
```{r}
tt_sub_final_w$total_asset_turnover <- 
  Winsorize(tt_sub_final_w$total_asset_turnover, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$total_asset_turnover)
hist(tt_sub_final_w$total_asset_turnover)
```

*w7* gross_profit_margin
```{r}
tt_sub_final_w$gross_profit_margin <- 
  Winsorize(tt_sub_final_w$gross_profit_margin, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$gross_profit_margin)
hist(tt_sub_final_w$gross_profit_margin)
```

*w8* net_profit_margin
```{r}
tt_sub_final_w$net_profit_margin <- 
  Winsorize(tt_sub_final_w$net_profit_margin, probs = c(0.025, 0.975))
#showing before and after:
hist(tt_sub_final$net_profit_margin)
hist(tt_sub_final_w$net_profit_margin)
```

*w9* current_ratio
```{r}
tt_sub_final_w$current_ratio <- 
  Winsorize(tt_sub_final_w$current_ratio, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$current_ratio)
hist(tt_sub_final_w$current_ratio)
```

*w10* debt_to_assets
```{r}
tt_sub_final_w$debt_to_assets <- 
  Winsorize(tt_sub_final_w$debt_to_assets, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$debt_to_assets)
hist(tt_sub_final_w$debt_to_assets)
```

*w11* debt_to_ebitda
```{r}
tt_sub_final_w$debt_to_ebitda <- 
  Winsorize(tt_sub_final_w$debt_to_ebitda, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$debt_to_ebitda)
hist(tt_sub_final_w$debt_to_ebitda)
```

*w12* interest_coverage
```{r}
tt_sub_final_w$interest_coverage <- 
  Winsorize(tt_sub_final_w$interest_coverage, probs = c(0.025, 0.975))
#showing before and after:
hist(tt_sub_final$interest_coverage)
hist(tt_sub_final_w$interest_coverage)
```

*w13* price_to_earnings
```{r}
tt_sub_final_w$price_to_earnings <- 
  Winsorize(tt_sub_final_w$price_to_earnings, probs = c(0.025, 0.975))
#showing before and after:
hist(tt_sub_final$price_to_earnings)
hist(tt_sub_final_w$price_to_earnings)
```

*w14* eps
```{r}
tt_sub_final_w$eps <- 
  Winsorize(tt_sub_final_w$eps, probs = c(0.025, 0.975))
#showing before and after:
hist(tt_sub_final$eps)
hist(tt_sub_final_w$eps)
```

*w15* dividend_yield 
```{r}
tt_sub_final_w$dividend_yield  <- 
  Winsorize(tt_sub_final_w$dividend_yield, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$dividend_yield )
hist(tt_sub_final_w$dividend_yield)
```

*w16* market_cap
```{r}
tt_sub_final_w$market_cap <- 
  Winsorize(tt_sub_final_w$market_cap, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$market_cap)
hist(tt_sub_final_w$market_cap)
```

*w17* n_employees
```{r}
tt_sub_final_w$n_employees <- 
  Winsorize(tt_sub_final_w$n_employees, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$n_employees)
hist(tt_sub_final_w$n_employees)
```

*w18* total_assets
```{r}
tt_sub_final_w$total_assets <- Winsorize(tt_sub_final_w$total_assets, probs = c(0.025, 0.975))
#showing before and after:
hist(tt_sub_final$total_assets)
hist(tt_sub_final_w$total_assets)
```

*w19* stock_volatility_2020
```{r}
tt_sub_final_w$stock_volatility_2020 <- Winsorize(tt_sub_final_w$stock_volatility_2020, probs = c(0.01, 0.99))
#showing before and after:
hist(tt_sub_final$stock_volatility_2020)
hist(tt_sub_final_w$stock_volatility_2020)
```

#-------------------------------------------------------------------------------
# Setting the names correct for reporting purposes
#-------------------------------------------------------------------------------
New dataframe:
```{r}
tt_sub_final_w_n <- tt_sub_final_w 
```

Setting the names correct:
```{r}
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'ESG_score_2020'] <- 'ESG score'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'decile_multiclass'] <- 'ESG decile'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'ESG_quartile'] <- 'ESG quartile'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'receivables_turnover'] <- 'Receivables turnover ratio'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'working_capital_turnover'] <- 'Working capital turnover ratio'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'total_asset_turnover'] <- 'Total asset turnover ratio'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'gross_profit_margin'] <- 'Gross profit margin'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'net_profit_margin'] <- 'Net profit margin'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'current_ratio'] <- 'Current ratio'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'debt_to_assets'] <- 'Debt-to-assets ratio'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'debt_to_ebitda'] <- 'Debt-to-EBITDA ratio'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'interest_coverage'] <- 'Interest coverage ratio'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'price_to_earnings'] <- 'Price-to-earnings ratio'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'eps'] <- 'Earnings per share'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'dividend_yield'] <- 'Dividend yield'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'market_cap'] <- 'Market capitalisation'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'n_employees'] <- 'Number of employees'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'total_assets'] <- 'Total assets'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'stock_volatility_2020'] <- 'Stock volatility'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'esg_data_availability_low'] <- 'ESG data availability low'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'esg_data_availability_middle'] <- 'ESG data availability middle'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'esg_data_availability_high'] <- 'ESG data availability high'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'country'] <- 'Country'
names(tt_sub_final_w_n)[names(tt_sub_final_w_n) == 'icb_sector_name'] <- 'Sector'
```

Removing irrelevant feature because of the new dummies:
```{r}
tt_sub_final_w_n$esg_data_availability <- NULL
```


#-------------------------------------------------------------------------------
# Final Descriptive Statistics
#-------------------------------------------------------------------------------

```{r}
stargazer(tt_sub_final_w_n, type="text", median = TRUE)
stargazer(tt_sub_final_w_n, median = TRUE)
```

#-------------------------------------------------------------------------------
# Final Correlation matrix
#-------------------------------------------------------------------------------

Correlation matrix with clear names and correct features:
```{r}
correlation_matrix_df <- tt_sub_final_w
correlation_matrix_df$decile_multiclass <- NULL
correlation_matrix_df$ESG_quartile <- NULL
correlation_matrix_df$esg_data_availability <- NULL

#checking the high correlation of the size features
print("size")
cor(correlation_matrix_df$total_assets, correlation_matrix_df$market_cap)
cor(correlation_matrix_df$n_employees, correlation_matrix_df$market_cap)

#checking the vif of total assets and market capitalisation
model <- lm(ESG_score_2020 ~ total_assets + market_cap, data = correlation_matrix_df)
print("VIF:")
VIF(model) #Below 5, not problematic

#checking the correlation among the ESG data availability dummies
#Not problematic: exclude one category for models (except trees)
print("availability")
cor(correlation_matrix_df$esg_data_availability_low, correlation_matrix_df$esg_data_availability_middle)
cor(correlation_matrix_df$esg_data_availability_low, correlation_matrix_df$esg_data_availability_high)
cor(correlation_matrix_df$esg_data_availability_middle, correlation_matrix_df$esg_data_availability_high)

#Creating correct names for report
names(correlation_matrix_df)[names(correlation_matrix_df) == 'ESG_score_2020'] <- 'ESG score'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'receivables_turnover'] <- 'Receivables turnover ratio'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'working_capital_turnover'] <- 'Working capital turnover ratio'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'total_asset_turnover'] <- 'Total asset turnover ratio'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'gross_profit_margin'] <- 'Gross profit margin'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'net_profit_margin'] <- 'Net profit margin'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'current_ratio'] <- 'Current ratio'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'debt_to_assets'] <- 'Debt-to-assets ratio'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'debt_to_ebitda'] <- 'Debt-to-EBITDA ratio'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'interest_coverage'] <- 'Interest coverage ratio'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'price_to_earnings'] <- 'Price-to-earnings ratio'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'eps'] <- 'Earnings per share'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'dividend_yield'] <- 'Dividend yield'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'market_cap'] <- 'Market capitalisation'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'n_employees'] <- 'Number of employees'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'total_assets'] <- 'Total assets'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'stock_volatility_2020'] <- 'Stock volatility'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'esg_data_availability_low'] <- 'ESG data availability low'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'esg_data_availability_middle'] <- 'ESG data availability middle'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'esg_data_availability_high'] <- 'ESG data availability high'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'country'] <- 'Country'
names(correlation_matrix_df)[names(correlation_matrix_df) == 'icb_sector_name'] <- 'Sector'

correlation_matrix_df %>% select_if(is.numeric) %>% 
  cor() %>% corrplot(tl.cex = 0.75)

```

#-------------------------------------------------------------------------------
#Diving into the correlations with ESG score
#-------------------------------------------------------------------------------
Constructing a table with only the correlations against the ESG score:
```{r}
correlation_dataframe <- as.data.frame(cor(select_if(correlation_matrix_df, is.numeric)))
correlation_dataframe_2 <- correlation_dataframe[1]
correlation_dataframe_2
```

Creating a table for LaTeX:
```{r}
xtable(correlation_dataframe_2, digits = 3)
```

#-------------------------------------------------------------------------------
#Correlations including sector and country dummies
#-------------------------------------------------------------------------------
Adding the columns for sector and country dummies (this is done through a recipe later on)
```{r}
tt_sub_final_w_n_dummies <- dummy_cols(tt_sub_final_w_n, select_columns= 'Sector', remove_first_dummy = FALSE)
tt_sub_final_w_n_dummies <- dummy_cols(tt_sub_final_w_n_dummies, select_columns= 'Country', remove_first_dummy = FALSE)
```

Removing decile and quartile because this is a correlation of 1:
```{r}
tt_sub_final_w_n_dummies$`ESG decile` <- NULL
tt_sub_final_w_n_dummies$`ESG quartile` <- NULL
```

Constructing a dataframe with all correlations including all the dummy columns:
```{r}
correlation_dataframe_dummies <- as.data.frame(cor(select_if(tt_sub_final_w_n_dummies, is.numeric)))
```

The dummy variables do not show high correlations.

Creating a table for LaTeX:
```{r}
correlation_dataframe_dummies_2 <- correlation_dataframe_dummies [1]
correlation_dataframe_dummies_2
xtable(correlation_dataframe_dummies_2, digits = 3)
```


#-------------------------------------------------------------------------------
# Create cleaned data csv for the machine learning models
#-------------------------------------------------------------------------------
```{r}
write.csv(tt_sub_final_w_n, "tt_sub_final_w_n.csv")
saveRDS(tt_sub_final_w_n, file = "tt_sub_final_w_n.rds")
```



#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------
*Expand data set*
#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------

#-------------------------------------------------------------------------------
#Data
#-------------------------------------------------------------------------------
Loading the data:
```{r}
expand <- read.csv("Expand_data_set_FINAL.csv", sep = ";")
head(expand)
```

#-------------------------------------------------------------------------------
#Subslection
#-------------------------------------------------------------------------------
Same subselection:
```{r}
subset_expand_final <- c("ISIN", "receivables_turnover", 
               "working_capital_turnover", "total_asset_turnover",
               "gross_profit_margin", "net_profit_margin", 
               "current_ratio", "debt_to_assets", 
               "debt_to_ebitda", "interest_coverage",
               "price_to_earnings", "eps", "dividend_yield",
               "market_cap", "n_employees", "total_assets",
               "icb_sector_name", 
               "country", "stock_volatility_2020",
               "esg_data_availability"
               )
expand_final <- expand[subset_expand_final]
head(expand_final)
```

#-------------------------------------------------------------------------------
#Frequency of categorical variables (same process):
#-------------------------------------------------------------------------------
Categorize values that were not in the training set to other, and the ones that
were categorized to other should be categorized as other.

*country*
```{r}
typeof(expand_final$country)
table(expand_final$country) 
table(expand_final$country) / length(expand_final$country)
```
Rule: <1% based on the train test set-> regroup to "Other"
BM
CZ
GI
GR
HU
IE
IM
JE
MT
PL
PT
LU

In addition for this data set (did not occur in train test data):
RO, LT, BG, HR, CY, EE, SI, MC, CS, IS

```{r}
expand_final$country <- recode(expand_final$country, 
       BM = "Other", 
       CZ = "Other", 
       GI = "Other", 
       GR = "Other", 
       HU = "Other", 
       IE = "Other", 
       IM = "Other", 
       JE = "Other",
       MT = "Other",
       PL = "Other",
       PT = "Other",
       LU = "Other",
       RO = "Other",
       LT = "Other",
       BG = "Other",
       HR = "Other",
       CY = "Other",
       EE = "Other",
       SI = "Other",
       MC = "Other",
       CS = "Other",
       IS = "Other")
```


```{r}
table(expand_final$country) 
table(expand_final$country) / length(expand_final$country)
```
It worked!

*icb_sector_name*
removing the spaces, - and commas
```{r}
expand_final$icb_sector_name <- gsub(" ", "_", expand_final$icb_sector_name)
expand_final$icb_sector_name <- gsub("-", "_", expand_final$icb_sector_name)
expand_final$icb_sector_name <- gsub(",", "", expand_final$icb_sector_name)
```

```{r}
table(expand_final$icb_sector_name)
```

Rule: <1% (23) -> regroup to other:
Investment_Banking_and_Brokerage_Services
Non_life_Insurance
Open_End_and_Miscellaneous_Investment_Vehicles
Precious_Metals_and_Mining
Real_Estate_Investment_Trusts
Tobacco
Waste_and_Disposal_Services
Alternative_Energy
Finance_and_Credit_Services
Real_Estate_Investment_and_Services

In addition for this data set:
Life_Insurance
```{r}
expand_final$icb_sector_name <- recode(expand_final$icb_sector_name,
       Investment_Banking_and_Brokerage_Services = "Other",
       Non_life_Insurance = "Other",
       Open_End_and_Miscellaneous_Investment_Vehicles = "Other",
       Precious_Metals_and_Mining = "Other",
       Real_Estate_Investment_Trusts = "Other",
       Tobacco = "Other",
       Waste_and_Disposal_Services = "Other",
       Alternative_Energy = "Other",
       Finance_and_Credit_Services = "Other",
       Real_Estate_Investment_and_Services = "Other",
       Life_Insurance = "Other")
```

```{r}
table(expand_final$icb_sector_name)
```
It worked.

#-------------------------------------------------------------------------------
# Adjustments for percentages
#-------------------------------------------------------------------------------
```{r}
expand_final$gross_profit_margin <- expand_final$gross_profit_margin / 100
expand_final$net_profit_margin <- expand_final$net_profit_margin / 100
expand_final$debt_to_assets <- expand_final$debt_to_assets / 100
expand_final$dividend_yield <- expand_final$dividend_yield / 100
```

#-------------------------------------------------------------------------------
# Converting ESG data availability to dummies
#-------------------------------------------------------------------------------
```{r}
expand_final$esg_data_availability_low <- ifelse(
  (round(expand_final$esg_data_availability,2) == 0.76) | 
    (expand_final$esg_data_availability == 0.0000000), 1, 0)
expand_final$esg_data_availability_middle <- ifelse(
  round(expand_final$esg_data_availability,2) == 0.95, 1, 0)
expand_final$esg_data_availability_high <- ifelse(expand_final$esg_data_availability == 1.0000000, 1, 0)
```

#-------------------------------------------------------------------------------
# Winsorizing
#-------------------------------------------------------------------------------
```{r}
expand_final_w <- expand_final
```

```{r}
expand_final_w$receivables_turnover <- Winsorize(expand_final_w$receivables_turnover, probs = c(0.01, 0.99))
expand_final_w$working_capital_turnover <- Winsorize(expand_final_w$working_capital_turnover, probs = c(0.01, 0.99))
expand_final_w$total_asset_turnover <- Winsorize(expand_final_w$total_asset_turnover, probs = c(0.01, 0.99))
expand_final_w$gross_profit_margin <- Winsorize(expand_final_w$gross_profit_margin, probs = c(0.01, 0.99))
expand_final_w$net_profit_margin <- Winsorize(expand_final_w$net_profit_margin, probs = c(0.025, 0.975))
expand_final_w$current_ratio <- Winsorize(expand_final_w$current_ratio, probs = c(0.01, 0.99))
expand_final_w$debt_to_assets <- Winsorize(expand_final_w$debt_to_assets, probs = c(0.01, 0.99))
expand_final_w$debt_to_ebitda <- Winsorize(expand_final_w$debt_to_ebitda, probs = c(0.01, 0.99))
expand_final_w$interest_coverage <- Winsorize(expand_final_w$interest_coverage, probs = c(0.025, 0.975))
expand_final_w$price_to_earnings <- Winsorize(expand_final_w$price_to_earnings, probs = c(0.025, 0.975))
expand_final_w$eps <- Winsorize(expand_final_w$eps, probs = c(0.025, 0.975))
expand_final_w$dividend_yield  <- Winsorize(expand_final_w$dividend_yield, probs = c(0.01, 0.99))
expand_final_w$market_cap <- Winsorize(expand_final_w$market_cap, probs = c(0.01, 0.99))
expand_final_w$n_employees <- Winsorize(expand_final_w$n_employees, probs = c(0.01, 0.99))
expand_final_w$total_assets <- Winsorize(expand_final_w$total_assets, probs = c(0.025, 0.975))
expand_final_w$stock_volatility_2020 <- Winsorize(expand_final_w$stock_volatility_2020, probs = c(0.01, 0.99))
```

#-------------------------------------------------------------------------------
# Setting the names correct
#-------------------------------------------------------------------------------
```{r}
expand_final_w_n <- expand_final_w
```


```{r}
names(expand_final_w_n)[names(expand_final_w_n) == 'ESG_score_2020'] <- 'ESG score'
names(expand_final_w_n)[names(expand_final_w_n) == 'decile_multiclass'] <- 'ESG decile'
names(expand_final_w_n)[names(expand_final_w_n) == 'ESG_quartile'] <- 'ESG quartile'
names(expand_final_w_n)[names(expand_final_w_n) == 'receivables_turnover'] <- 'Receivables turnover ratio'
names(expand_final_w_n)[names(expand_final_w_n) == 'working_capital_turnover'] <- 'Working capital turnover ratio'
names(expand_final_w_n)[names(expand_final_w_n) == 'total_asset_turnover'] <- 'Total asset turnover ratio'
names(expand_final_w_n)[names(expand_final_w_n) == 'gross_profit_margin'] <- 'Gross profit margin'
names(expand_final_w_n)[names(expand_final_w_n) == 'net_profit_margin'] <- 'Net profit margin'
names(expand_final_w_n)[names(expand_final_w_n) == 'current_ratio'] <- 'Current ratio'
names(expand_final_w_n)[names(expand_final_w_n) == 'debt_to_assets'] <- 'Debt-to-assets ratio'
names(expand_final_w_n)[names(expand_final_w_n) == 'debt_to_ebitda'] <- 'Debt-to-EBITDA ratio'
names(expand_final_w_n)[names(expand_final_w_n) == 'interest_coverage'] <- 'Interest coverage ratio'
names(expand_final_w_n)[names(expand_final_w_n) == 'price_to_earnings'] <- 'Price-to-earnings ratio'
names(expand_final_w_n)[names(expand_final_w_n) == 'eps'] <- 'Earnings per share'
names(expand_final_w_n)[names(expand_final_w_n) == 'dividend_yield'] <- 'Dividend yield'
names(expand_final_w_n)[names(expand_final_w_n) == 'market_cap'] <- 'Market capitalisation'
names(expand_final_w_n)[names(expand_final_w_n) == 'n_employees'] <- 'Number of employees'
names(expand_final_w_n)[names(expand_final_w_n) == 'total_assets'] <- 'Total assets'
names(expand_final_w_n)[names(expand_final_w_n) == 'stock_volatility_2020'] <- 'Stock volatility'
names(expand_final_w_n)[names(expand_final_w_n) == 'esg_data_availability_low'] <- 'ESG data availability low'
names(expand_final_w_n)[names(expand_final_w_n) == 'esg_data_availability_middle'] <- 'ESG data availability middle'
names(expand_final_w_n)[names(expand_final_w_n) == 'esg_data_availability_high'] <- 'ESG data availability high'
names(expand_final_w_n)[names(expand_final_w_n) == 'country'] <- 'Country'
names(expand_final_w_n)[names(expand_final_w_n) == 'icb_sector_name'] <- 'Sector'
```

```{r}
tt_sub_final_w_n$esg_data_availability <- NULL
```

#-------------------------------------------------------------------------------
# Descriptive Statistics Expand Data set
#-------------------------------------------------------------------------------
```{r}
stargazer(expand_final_w_n, type = "text", median = TRUE)
stargazer(expand_final_w_n, median = TRUE)
```

#-------------------------------------------------------------------------------
# Create cleaned data csv for the best machine learning model
#-------------------------------------------------------------------------------
```{r}
write.csv(expand_final_w_n, "expand_final_w_n.csv")
saveRDS(expand_final_w_n, file = "expand_final_w_n.rds")
```

*End*
