---
title: "R Notebook E 447614 BAM Thesis - Quartiles"
author: "447614"
output: html_notebook
---
09-07-2022

#-------------------------------------------------------------------------------
#Packages
#-------------------------------------------------------------------------------
```{r}
library("tidymodels")
library("readr")
library("knitr")
library("skimr")
library("corrplot")
library("stargazer")
library("dplyr")
library("DescTools")
library("glmnet")
library("leaps")
library("doParallel")
library("themis")
library("xgboost")
library("ranger")
library("vip")
library("ggridges")
library("forcats")
library("neuralnet")
```

#-------------------------------------------------------------------------------
#Data
#-------------------------------------------------------------------------------
Loading the data:
```{r}
tt_sub_final_w_n <- readRDS(file = "tt_sub_final_w_n.rds")
head(tt_sub_final_w_n)
```

Checking the descriptives:
```{r}
stargazer(tt_sub_final_w_n, type = "text", median = TRUE)
```

#Factor
Setting the dependent variable as a factor
```{r}
tt_sub_final_w_n$`ESG quartile` <- as.factor(tt_sub_final_w_n$`ESG quartile`)
str(tt_sub_final_w_n$`ESG quartile`)
typeof(tt_sub_final_w_n$`ESG quartile`)
```

#-------------------------------------------------------------------------------
# (Im)Balance
#-------------------------------------------------------------------------------
Checking the imbalance:
```{r}
tt_sub_final_w_n %>% count(`ESG quartile`) %>% 
  mutate(prop = n / sum(n))
```


#-------------------------------------------------------------------------------
# Metrics
#-------------------------------------------------------------------------------
```{r}
class_metrics <- metric_set(accuracy, sensitivity, specificity, precision, roc_auc, kap, f_meas, bal_accuracy)
```

#-------------------------------------------------------------------------------
# Split
#-------------------------------------------------------------------------------

#Train-validation-test split
70% for training, 30% for testing
Including a stratified split, makes sure that there is balance between train and 
test set to ensure a similar representation.
```{r}
set.seed(7777)
tt_split <- initial_split(tt_sub_final_w_n, prop = 0.7, strata = `ESG quartile`)
tt_split
```

Creating the dataframes for train and test:
```{r}
tt_train <- training(tt_split)
tt_test  <- testing(tt_split)
```

#Checking the balance
```{r}
tt_train %>% count(`ESG quartile`) %>% 
  mutate(prop = n / sum(n))
tt_test %>% count(`ESG quartile`) %>% 
  mutate(prop = n / sum(n))
```
The distribution is approximately the same among the train and test set.

#CV
For model tuning (validation test), a 5-fold cross-validation (CV) is employed. 
The following code creates the CV folds, through a stratified split, out of the train set:
```{r}
set.seed(8225)
cv_folds <- tt_train %>% 
  vfold_cv(v =5, strata = `ESG quartile`)
cv_folds
```


#-------------------------------------------------------------------------------
# Standard recipe for all
#-------------------------------------------------------------------------------

*standard_recipe*
```{r}
standard_recipe <- 
  recipe(`ESG quartile` ~ 
           #Activity:
           `Receivables turnover ratio` + `Working capital turnover ratio` + `Total asset turnover ratio` +
           #Profitability:
           `Gross profit margin` + `Net profit margin` + 
           #Liquidity:
           `Current ratio` + 
           #Solvency:
           `Debt-to-assets ratio` + `Debt-to-EBITDA ratio` + `Interest coverage ratio` + 
           #Valuation:
           `Price-to-earnings ratio` + `Earnings per share` + `Dividend yield` + 
           #Size:
           `Market capitalisation` + `Number of employees` + `Total assets` + 
           #characteristics:
           `Sector` + `Country` + `Stock volatility` +
           #ESG data availability:
           `ESG data availability low` + `ESG data availability middle` #for trees add: (ESG data availability high)
         #Data:
         , data = tt_train) %>%
  #Dummies:
  step_dummy(`Sector`, `Country`) %>% #for trees add: , one_hot = TRUE
  #Log transformation:
  step_log(`Market capitalisation`, `Number of employees`, `Total assets`, `Stock volatility`) %>%
  #Normalization:
  step_normalize(`Receivables turnover ratio`, `Working capital turnover ratio`, `Total asset turnover ratio`,
                 `Gross profit margin`, `Net profit margin`, 
                 `Current ratio`,
                 `Debt-to-assets ratio`, `Debt-to-EBITDA ratio`, `Interest coverage ratio`,
                 `Price-to-earnings ratio`, `Earnings per share`, `Dividend yield`, 
                 `Market capitalisation`, `Number of employees`, `Total assets`,
                 `Stock volatility`)
standard_recipe 
```

Seeing how it looks like on the data set:
```{r}
train_baked <- standard_recipe  %>% prep(tt_train)
train_baked %>% head()
```

*tree_recipe*
For a tree: adding the high availability and the one_hot=TRUE to show all categorical variables as a dummy
```{r}
tree_recipe <- 
  recipe(`ESG quartile` ~ 
           #Activity:
           `Receivables turnover ratio` + `Working capital turnover ratio` + `Total asset turnover ratio` +
           #Profitability:
           `Gross profit margin` + `Net profit margin` + 
           #Liquidity:
           `Current ratio` + 
           #Solvency:
           `Debt-to-assets ratio` + `Debt-to-EBITDA ratio` + `Interest coverage ratio` + 
           #Valuation:
           `Price-to-earnings ratio` + `Earnings per share` + `Dividend yield` + 
           #Size:
           `Market capitalisation` + `Number of employees` + `Total assets` + 
           #characteristics:
           `Sector` + `Country` + `Stock volatility` +
           #ESG data availability:
           `ESG data availability low` + `ESG data availability middle` + `ESG data availability high`
         #Data:
         , data = tt_train) %>%
  #Dummies:
  step_dummy(Sector, Country, one_hot = TRUE) %>% 
  #Log transformation:
  step_log(`Market capitalisation`, `Number of employees`, `Total assets`, `Stock volatility`) %>%
  #Normalization:
  step_normalize(`Receivables turnover ratio`, `Working capital turnover ratio`, `Total asset turnover ratio`,
                 `Gross profit margin`, `Net profit margin`, 
                 `Current ratio`,
                 `Debt-to-assets ratio`, `Debt-to-EBITDA ratio`, `Interest coverage ratio`,
                 `Price-to-earnings ratio`, `Earnings per share`, `Dividend yield`, 
                 `Market capitalisation`, `Number of employees`, `Total assets`,
                 `Stock volatility`)
tree_recipe 
```

Seeing how it looks like on the data set:
```{r}
train_baked <- tree_recipe  %>% prep(tt_train)
train_baked %>% head()
```

This is correct, went from 64 columns to 67 (esg_data_availability_high, sector, country)


#-------------------------------------------------------------------------------
#Modelling
#-------------------------------------------------------------------------------

#--------------------------
# 1: Multinomial regression (logistic) LASSO
#--------------------------

#Recipe:
```{r}
standard_recipe
```

#Model:
`alpha = 1` = lasso penalty
`alpha = 0` = ridge penalty
```{r}
logistic_model_lasso <- multinom_reg(penalty = tune(), mixture = 1) %>%
  set_engine("glmnet", importance = "impurity") %>%
  set_mode("classification")
```

#Workflow:
```{r}
logistic_lasso_mod_workflow <- 
  workflow() %>% 
  add_model(logistic_model_lasso) %>% 
  add_recipe(standard_recipe)
```

#Tuning:
Define tuning process
```{r}
model_control <- control_grid(save_pred = TRUE)
```

Grid:
```{r}
lasso_logistic_grid <- grid_regular(parameters(logistic_model_lasso), levels = 50)
lasso_logistic_grid
```


Tune:
```{r}
tune_res_lasso <- tune_grid(
  logistic_model_lasso,
  standard_recipe,
  grid = lasso_logistic_grid,
  control = model_control,
  metrics = class_metrics,
  resamples = cv_folds
)
```

Save tuning results:
```{r}
save(tune_res_lasso, file = "quartile_tune_lasso")
```

Results:
```{r}
lasso_tune_metrics <- tune_res_lasso %>% collect_metrics()
lasso_tune_metrics
```

Plot:
```{r}
lasso_tune_metrics %>% filter(.metric == "roc_auc") %>% 
  ggplot(aes(x = penalty, y = mean, 
             ymin = mean - std_err, ymax = mean + std_err)) + 
  geom_linerange(alpha = 0.5) + 
  geom_point() + 
  scale_x_log10() + 
  labs(y = "roc auc", x = expression(lambda))

lasso_tune_metrics %>% filter(.metric == "accuracy") %>% 
  ggplot(aes(x = penalty, y = mean, 
             ymin = mean - std_err, ymax = mean + std_err)) + 
  geom_linerange(alpha = 0.5) + 
  geom_point() + 
  scale_x_log10() + 
  labs(y = "accuracy", x = expression(lambda))
```

Select best model through the one standard error rule:
```{r}
lin_class_best_model_lasso <-  select_by_one_std_err(tune_res_lasso, metric = "roc_auc", desc(penalty))
lin_class_best_model_lasso
```

#Finalize workflow:
```{r}
reg_class_lasso_workflow_final <- 
  logistic_lasso_mod_workflow %>% 
  finalize_workflow(lin_class_best_model_lasso)
reg_class_lasso_workflow_final 
```

#Test:
On the test set:
```{r}
lr_lasso_last_fit <- reg_class_lasso_workflow_final %>% 
  last_fit(tt_split, 
           metrics = class_metrics)
```

Results:
```{r}
lr_lasso_metrics <- lr_lasso_last_fit %>% collect_metrics()
lr_lasso_metrics
```

#--------------------------------------------
# 2.0: Multinomial logistic regression RIDGE
#--------------------------------------------

#Recipe:
```{r}
standard_recipe
```

#Model:
`alpha = 1` = lasso penalty
`alpha = 0` = ridge penalty
```{r}
logistic_model_ridge <- multinom_reg(penalty = tune(), mixture = 0) %>%
  set_engine("glmnet", importance = "impurity") %>%
  set_mode("classification")
```

#Workflow:
```{r}
logistic_mod_ridge_workflow <- 
  workflow() %>% 
  add_model(logistic_model_ridge) %>% 
  add_recipe(standard_recipe)
```

#Tuning:
Define tuning process:
```{r}
model_control <- control_grid(save_pred = TRUE)
```

Grid:
```{r}
logistic_grid_ridge <- grid_regular(parameters(logistic_model_ridge), levels = 50)
logistic_grid_ridge
```

Tune:
```{r}
tune_res_ridge <- tune_grid(
  logistic_model_ridge,
  standard_recipe,
  grid = logistic_grid_ridge,
  control = model_control,
  metrics = class_metrics,
  resamples = cv_folds
)
```

Save tuning results:
```{r}
save(tune_res_ridge, file = "quartile_tune_ridge")
```

Results:
```{r}
ridge_tune_metrics <- tune_res_ridge %>% collect_metrics()
ridge_tune_metrics
```

Plot:
```{r}
ridge_tune_metrics %>% filter(.metric == "roc_auc") %>% 
  ggplot(aes(x = penalty, y = mean, 
             ymin = mean - std_err, ymax = mean + std_err)) + 
  geom_linerange(alpha = 0.5) + 
  geom_point() + 
  scale_x_log10() + 
  labs(y = "roc auc", x = expression(lambda))

ridge_tune_metrics %>% filter(.metric == "accuracy") %>% 
  ggplot(aes(x = penalty, y = mean, 
             ymin = mean - std_err, ymax = mean + std_err)) + 
  geom_linerange(alpha = 0.5) + 
  geom_point() + 
  scale_x_log10() + 
  labs(y = "accuracy", x = expression(lambda))
```


Select best model through the one standard error rule:
```{r}
lin_class_best_model_ridge <-  select_by_one_std_err(tune_res_ridge, metric = "roc_auc", desc(penalty))
lin_class_best_model_ridge
```

#Finalize workflow:
```{r}
reg_class_ridge_workflow_final <- 
  logistic_mod_ridge_workflow %>% 
  finalize_workflow(lin_class_best_model_ridge)
reg_class_ridge_workflow_final
```

#Test:
On the test set:
```{r}
lr_ridge_last_fit <- reg_class_ridge_workflow_final %>% 
  last_fit(tt_split, 
           metrics = class_metrics)
```

Results:
```{r}
lr_ridge_metrics <- lr_ridge_last_fit %>% collect_metrics()
lr_ridge_metrics
```


#--------------------------
# 3: k-NN
#--------------------------

#Recipe:
```{r}
standard_recipe
```

#Model:
```{r}
knn_class_mod <- nearest_neighbor(neighbors = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("kknn", importance = "impurity")
```

#Workflow:
```{r}
knn_class_workflow <-
  workflow() %>% 
  add_model(knn_class_mod) %>% 
  add_recipe(standard_recipe)
knn_class_workflow
```

#Tuning:

Tuning grid:
```{r}
knn_class_tune_grid <- tibble(neighbors = 5:100*5 + 1)
knn_class_tune_grid
```

Tuning:
```{r}
knn_tune_res <- tune_grid(
  knn_class_mod ,
  standard_recipe,
  grid = knn_class_tune_grid,
  metrics = class_metrics,
  resamples = cv_folds
)
```

Save tuning results:
```{r}
save(knn_tune_res, file = "quartile_tune_knn")
```

Results:
```{r}
knn_tune_metrics <- knn_tune_res %>% collect_metrics()
knn_tune_metrics
```

Plot::
```{r}
knn_tune_metrics %>% 
  ggplot(aes(x = neighbors, y = mean)) + 
  geom_point() + geom_line() + 
  facet_wrap(~ .metric, scales = "free_y")
```

Select best model through the one standard error rule:
```{r}
knn_class_best_model <- select_by_one_std_err(knn_tune_res, metric = "roc_auc", desc(neighbors))
knn_class_best_model
```

#Finalize workflow:
```{r}
knn_class_workflow_final <- 
  knn_class_workflow %>% 
  finalize_workflow(knn_class_best_model)
knn_class_workflow_final 
```

#Test:
On the test set:
```{r}
knn_last_fit <- knn_class_workflow_final  %>% 
  last_fit(tt_split, 
           metrics = class_metrics)
```

Results:
```{r}
knn_metrics <- knn_last_fit %>% collect_metrics()
knn_metrics
```

#--------------------------
# 4: XGB (Gradient Boosting)
#--------------------------

#Recipe:
```{r}
tree_recipe
```

#Model:
```{r}
xgb_model_tune <- 
  boost_tree(trees = tune(), tree_depth = tune(), 
             learn_rate = tune(), stop_iter = 500) %>%
  set_mode("classification") %>%
  set_engine("xgboost", importance = "impurity")
```

#Workflow:
```{r}
xgb_wf <- workflow() %>%
  add_recipe(tree_recipe) %>%
  add_model(xgb_model_tune)
xgb_wf
```

#Tuning:
Speed up computation:
```{r}
registerDoParallel()
```

Tuning grid:
```{r}
xgb_grid <- expand.grid(trees = 500 * 1:20, 
                        learn_rate = c(0.1, 0.01), 
                        tree_depth = 1:5*2)
xgb_grid
```

Performing grid search:
```{r}
xgb_tune_res <- tune_grid(
  xgb_wf,
  resamples = cv_folds,
  grid = xgb_grid,
  metrics = class_metrics
)
```

Save tuning results:
```{r}
save(xgb_tune_res, file = "quartile_tune_xgb")
```

Extract the metrics:
```{r}
xgb_tune_metrics <- xgb_tune_res %>%
  collect_metrics()
xgb_tune_metrics
```

Selecting the best model through the one standard error rule:
```{r}
xgb_model <- select_by_one_std_err(xgb_tune_res, metric = "roc_auc", trees)
xgb_model
```

#Finalize workflow:
```{r}
xgb_final_wf <- 
  xgb_wf %>% 
  finalize_workflow(xgb_model)
xgb_final_wf
```

#Test:
On the test set:
```{r}
xgb_final_fit <- xgb_final_wf %>%
  last_fit(tt_split, metrics = class_metrics)
```

Results:
```{r}
xgb_metrics <- xgb_final_fit %>%
  collect_metrics()
xgb_metrics
```

#--------------------------
# 5: Random Forest
#--------------------------

#Recipe:
```{r}
tree_recipe
```

#Model:
```{r}
rf_model_tune <- rand_forest(mtry = tune(), trees = 2500) %>%
  set_mode("classification") %>%
  set_engine("ranger", importance = "impurity")
```

#Workflow:
```{r}
rf_wf <- workflow() %>%
  add_recipe(tree_recipe) %>%
  add_model(rf_model_tune)
rf_wf
```

#Tuning:

For speeding up the process:
```{r}
registerDoParallel()
```

Tuning with a tuning grid equal to the length of the number of parameters:
```{r}
set.seed(99154345)
rf_tune_res <- tune_grid(
  rf_wf,
  resamples = cv_folds,
  grid = tibble(mtry = 1:66),
  metrics = class_metrics
)
rf_tune_res
```

Save tuning results:
```{r}
save(rf_tune_res, file = "quartile_tune_rf")
```

Collecting the metrics:
```{r}
rf_tune_res %>%
  collect_metrics()
```

Plot:
```{r}
rf_metrics <- rf_tune_res %>% collect_metrics()
rf_metrics %>%
  ggplot(aes(x = mtry, y = mean,
             ymin = mean - std_err, ymax = mean + std_err)) +
  geom_errorbar(width = 0.1) +
  geom_point() +
  facet_wrap(~ .metric, scale = "free_y")
```

Selecting the best one though the one standard error rule:
```{r}
rf_model <- select_by_one_std_err(rf_tune_res, metric = "roc_auc", mtry)
rf_model
```

#Finalize workflow:
```{r}
rf_final_wf <- 
  rf_wf %>% 
  finalize_workflow(rf_model)
rf_final_wf
```

#Test:
On the test set:
```{r}
rf_final_fit <- rf_final_wf %>%
  last_fit(tt_split, metrics = class_metrics)
```

Metrics:
```{r}
rf_metrics <- rf_final_fit %>%
  collect_metrics()
rf_metrics
```

#--------------------------------------------------------------------
# Most important features for the best model (random forest): 
#--------------------------------------------------------------------

```{r}
rf_classification_important_features <- rf_final_fit %>% 
  extract_fit_parsnip() %>% 
  vip(num_features = 20)
rf_classification_important_features
```

#--------------------------------------------------------------------
# Error analysis on test set for best performing model: random forest
#--------------------------------------------------------------------
Creating a dataframe with the prediction and the true ESG quartile:
```{r}
predictions_all <- rf_final_fit$.predictions
my_df <- as.data.frame(predictions_all)
df_predicted_actual <- my_df[c(".pred_class", "ESG.quartile")] 
df_predicted_actual
```

Creating a column stating whether it is a correct prediction, a column with the absolute difference, and calculating the accuracy besides the number of predictions.
```{r}
df_predicted_actual$correct <- ifelse(df_predicted_actual$.pred_class == df_predicted_actual$ESG.quartile, 1, 0)
df_predicted_actual$abs_diff <- abs(as.numeric(as.numeric(df_predicted_actual$.pred_class) - as.numeric(df_predicted_actual$ESG.quartile)))
df_predicted_actual
#checking the accuracy
print("accuracy is:")
sum(df_predicted_actual$correct)/length(df_predicted_actual$correct) #is correct, same accuracy
#stats
print("number of predictions is:")
length(df_predicted_actual$correct)
```

Filter on incorrect predictions:
```{r}
df_predicted_actual_incorrect <- df_predicted_actual[df_predicted_actual$correct == 0, ]
df_predicted_actual_incorrect
```
Performing calculations:
```{r}
#number of incorrect predictions
n_incorrect <- length(df_predicted_actual_incorrect$abs_diff)
n_incorrect

#1 classes from the true one
df_predicted_actual_incorrect_pred_1 <- df_predicted_actual_incorrect[df_predicted_actual_incorrect$abs_diff == 1, ]
num_abs_diff_1 <- length(df_predicted_actual_incorrect_pred_1$abs_diff)
num_abs_diff_1

#2 classes from the true one
df_predicted_actual_incorrect_pred_2 <- df_predicted_actual_incorrect[df_predicted_actual_incorrect$abs_diff == 2, ]
num_abs_diff_2 <- length(df_predicted_actual_incorrect_pred_2$abs_diff)
num_abs_diff_2

#total check
num_abs_diff_1 + num_abs_diff_2
```

```{r}
print(paste("For the", n_incorrect, "incorrect predictions"))
print(paste(num_abs_diff_1,"deviate one class, which is", (num_abs_diff_1/n_incorrect), "percent"))
print(paste(num_abs_diff_2,"deviate two classes, which is", (num_abs_diff_2/n_incorrect), "percent"))
```

#-------------------------------------------------------------------------------
#Fit to the expand data set to the widen the ESG stock universe
#-------------------------------------------------------------------------------
Loading the expand data set:
```{r}
expand_final_w_n<- readRDS(file = "expand_final_w_n.rds")
head(expand_final_w_n)
```

Performing the random forest model:
```{r}
set.seed(5555)
fit_wf_final_rf <- fit(rf_final_wf, tt_train)
final_pred_rf <- predict(fit_wf_final_rf, expand_final_w_n)
head(final_pred_rf)
```

Subtracting the predictions:
```{r}
list_pred <- as.data.frame(final_pred_rf)
list_pred$.pred
```

Creating a dataframe with the .pred and the ISIN:
```{r}
expand_final_w_n$rf_pred <- list_pred$.pred
head(expand_final_w_n)
```

Creating a dataframe with the ISIN and the predictions for the 1,742 stocks
```{r}
expand_quartiles_rf_pred <- expand_final_w_n[c("ISIN", "rf_pred")]
head(expand_quartiles_rf_pred)
```

To csv:
```{r}
write.csv(expand_quartiles_rf_pred, "expand_ESG_quartile_rf_pred_09_07_2022.csv")
```

*End* 
